\documentclass[11pt,letterpaper,ragged2e]{altacv}
\geometry{left=1cm,right=9cm,marginparwidth=6.8cm,marginparsep=1.2cm,top=1cm,bottom=1.25cm}
\ifxetexorluatex
  \setmainfont{Carlito}
\else
  \usepackage[utf8]{inputenc}
  \usepackage[T1]{fontenc}
  \usepackage[default]{lato}
\fi

\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}


\begin{document}
\name{KLAIRE CURDE}
% \tagline{Software Engineer looking to apply unique and diverse experience to a full time position.}
\tagline{}
\personalinfo{%
  \email{\href{mailto:kcurde@gmail.com}{kcurde@gmail.com}}
  \phone{\href{tel:724-718-7281}{(724) 718-7281}}
  \github{\href{https://github.com/klairecodes}{github.com/klairecodes}}
  \linkedin{\href{https://www.linkedin.com/in/klaire-curde/}{linkedin.com/in/klaire-curde}}
  \site{\href{https://klaire.codes/}{klaire.codes}}
}

% Ideally these wouldn't be here...
\hbadness=1960 % Suppresses a specific underfull hbox error in the sidebar
\hfuzz=5pt % Suppresses a specific overfull hbox error in the personalinfo header

%% Make the header extend all the way to the right
\begin{fullwidth}
  \makecvheader
\end{fullwidth}

%% Make fonts of itemize environments slightly smaller
\AtBeginEnvironment{itemize}{\small}


%% EXPERIENCE %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Provide the file name containing the sidebar contents as an optional parameter to \cvsection.
\cvsection[sidebar]{EXPERIENCE}

\cvexperience{Software Engineer Co-op}{Bryx Inc.}
{
  \begin{itemize}
    \item Enhanced an EMS/firefighter job submission page with a modern stack.
    \item Migrated from class-based to efficient functional React + TypeScript.
    \item Focused on reliability, and integrated extensive first responder feedback.
  \end{itemize}
}
{\faCalendar\, Summer 2023}
{
  \cvtag{TypeScript}\cvtag{React}\cvtag{Semantic UI}\cvtag{SQL}
}


\cvexperience{DevOps Engineer Co-op}{Council Rock}
{
  \begin{itemize}
    \item Maintained an RKE Kubernetes deployment of the Thingsboard IoT application with custom modifications.
    \item Developed a new Docker Compose deployment for external services.
    \item Managed a Proxmox cluster, and created optimized multi-stage Docker BuildKit builds.
  \end{itemize}
}
{\faCalendar\, May 2022 - August 2022}
{
  \cvtag{Kubernetes}\cvtag{Docker}\cvtag{Docker Compose}\cvtag{AWS}\cvtag{Proxmox}
}

\cvexperience{Software Engineer Co-op}{Council Rock}
{
  \begin{itemize}
    \item Implemented the CoAP protocol in C++ using the libcoap C library.
    \item Integrated with ThingsBoard IoT Software's REST API via CoAP.
  \end{itemize}
}
{\faCalendar\, Aug 2021 - Dec 2021}
{
  \cvtag{C++}\cvtag{C}\cvtag{Linux}\cvtag{CoAP}\cvtag{IoT}
}

\cvexperience{Software Engineer Co-op}{LightRiver Software}
{
  \begin{itemize}
    \item Designed and implemented an ingress controller in C using a reverse proxy with Apache for REST API requests.
    \item Enhanced the netFLEX application with new features using C, JavaScript, and JSON on Linux.
  \end{itemize}
}
{\faCalendar\, Jun 2021 - Aug 2021}
{
  \cvtag{C}\cvtag{Linux}\cvtag{Apache}\cvtag{PostgreSQL}\cvtag{HTML/CSS}\cvtag{JS}
}


%% PROJECTS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Projects}

\cvproject{Server Room Rebuild}{{\faGoogle} \,\href{https://cloud.google.com/blog/transform/wayfair-server-donation-mass-open-cloud-rit-student-innovation-johonnot}{cloud.google.com}}
{
  \begin{itemize}
    \item Led and organized an \href{https://www.rit.edu/news/wayfair-gifts-850000-servers-rits-computer-science-house}{\textbf{\$850,000+ server hardware donation}} from Wayfair's decommissioned datacenter for 9 months.
    \item Installed over \textbf{three dozen} machines from scratch running \textbf{1150 k8s pods for 400 projects, 170 VMs, and 500 terabytes of Ceph storage.}
  \end{itemize}
}
{
  \cvtag{Kubernetes}\cvtag{Proxmox}\cvtag{Ceph}\cvtag{FreeIPA}\cvtag{Docker}\cvtag{OKD}\cvtag{Linux}
}

\cvproject{Sparsr}{{\faGithub} \,\href{https://github.com/klairecodes/sparsr}{github.com/klairecodes/sparsr}}
{
  \begin{itemize}
    \item Utilized the OpenCV Python API and Whisper AI to capture timestamps and screenshots of where a searched phrase was said in any video.
  \end{itemize}
}
{
  \cvtag{Python}\cvtag{OpenCV}\cvtag{Whisper AI}\cvtag{Podman}
}

%\cvproject{Guestbook}{{\faGithub} \,\href{https://github.com/klairecodes/guestbook}{github.com/klairecodes/guestbook}}
%{
%\begin{itemize}
%\item Created a content delivery application for cabin guestbooks using protocol buffers, sqlx, and the highly scalable Rust Tokio runtime.
%\end{itemize}
%}
%{
%\cvtag{Rust}\cvtag{gRPC}\cvtag{Protobuf}\cvtag{Podman}\cvtag{SQLx}\cvtag{S3}
%}

\cvproject{Kevlar}{{\faGithub} \,\href{https://github.com/klairecodes/kevlar}{github.com/klairecodes/guestbook}}
{
  \begin{itemize}
    \item Implemented user-initiated channel blacklist capabilities for Slack.
          % \item Employed best practices for API use, and included extensive documentation for use in any workspace.
  \end{itemize}
}
{
  \cvtag{Python}\cvtag{Podman}\cvtag{Kubernetes}\cvtag{Slack Bolt API}\cvtag{OKD}
}

% \cvproject{RITlinks}
% {
%   {\faLink} \,\href{https://ritlinks.csh.rit.edu}{https://ritlinks.csh.rit.edu}\quad
%   {\faGithub} \,\href{https://github.com/klairecodes/ritlinks}{github.com/klairecodes/ritlinks}
% }
% {
%   \begin{itemize}
%     %\item Developed a website using Django and custom Bootstrap 4 templates to dynamically generate a list of all the websites RIT makes available to students as well as their uses.
%     \item Developed a site to dynamically generate a list of all websites RIT makes available to students and their uses.
%     \item Deployed on an OKD 4 Kubernetes cluster.
%   \end{itemize}
% }
% {
%   \cvtag{Python}\cvtag{Django}\cvtag{Docker}\cvtag{OKD}\cvtag{Boostrap 4}
% }


\clearpage

\nocite{*}

\end{document}
