\vspace{1.5pt} % makes the section lines even

\cvsection{Education}
\cvedu{{\faSchool} \textbf{Rochester Institute of Technology}}
{B.S. in Computer Science}{Earned May 2024}
{Psychology Immersion}
{AI/ML/LLM \& Intelligent Security Concentration}

\cvsection{Skills}
\cvsubsection{Languages}
\cvtag{Python}
\cvtag{C}
\cvtag{C++}
\cvtag{Rust}
\cvtag{JavaScript}
\cvtag{TypeScript}
\cvtag{Java}
\cvtag{Go}
\cvtag{Bash}
\cvtag{HTML/CSS}
\cvtag{SQL}
\cvtag{\LaTeX}

\smallskip

\cvsubsection{Tools}
\cvtag{Linux}
\cvtag{Docker}
\cvtag{Nginx}
\cvtag{Kubernetes}
\cvtag{Openshift/OKD}
\cvtag{Proxmox}
\cvtag{Ceph}
\cvtag{PostgreSQL}
\cvtag{Django}
\cvtag{AWS}
\cvtag{Protobuf}
\cvtag{gRPC}
\cvtag{DataDog}
\cvtag{Puppet}

\cvsection{Activities}
\cvactivity{{\faLaptopCode} Computer Science House}
{
	{SysAdmin Director}    \hfill\adate{May 2021 - Oct 2022}\newline
}
{
	\item{Led a \href{https://www.rit.edu/news/wayfair-gifts-850000-servers-rits-computer-science-house}{\textbf{\$1.2 million+ server hardware donation}} from Wayfair's decommissioned datacenter,} featured in a \href{https://cloud.google.com/blog/transform/wayfair-server-donation-mass-open-cloud-rit-student-innovation-johonnot}{\textbf{Google Cloud article}}.
	\item{\textbf{Rebuilt an enterprise-grade datacenter} with modern hardware, setting up over \textbf{three dozen} machines from scratch running \textbf{1150 k8s pods for 400 projects, 170 VMs, and 500 terabytes of Ceph storage.}}
	%\item{Maintaining technologies including an OKD 4 Kubernetes cluster, Proxmox cluster, FreeIPA user management, Ceph distributed storage, multiple databases, mail server, MediaWiki instance, and various web services.}
	\item{Led a team of eight admins for \textbf{two years}, and spent \textbf{five total years} maintaining the datacenter for over 100 active users.}
}

\cvactivity{{\faCameraRetro} Reporter Magazine}
{
	{Sysadmin} \hfill\adate{May 2021 - May 2023}\newline
}
{
	\item{Maintained the frontend and infrastructure for a student-run magazine.}
	\item{Supported \textbf{30+ contributors} and the \textbf{entire student body} audience.}
	\item{Ensured maximum uptime with automatic certificate renewals, planned Drupal upgrades, and clear communication.}
}

\cvactivity{{\faSchool} RIT Residence Life}
{
	{Resident Advisor} \hfill\adate{Aug 2020 - May 2021}\newline
}
{
	\item{Supported and guided \textbf{50 dorm residents.}}
	\item{Responsible for their health and safety.}
}

\cvactivityshort{{ \faWineGlass}{ } WSET Level 2 Wine Certification}
{
	%{Completed with Merit} \hfill\adate{May 2024}\newline
}
%{\item{Demonstrated knowledge of various wine regions, grape varieties, and wine tasting techniques.}}
{\item{Demonstrated knowledge of various wine regions, grape varieties, and wine tasting techniques.}}

%\cvmultiactivitycsh{Computer Science House \faLaptopCode}
%{SysAdmin Director}{May 2021 - Oct 2022}
%{System Administrator}{Oct 2020 - Present}
%{Member}{Aug 2019 - Present}
%{•  Organized a \href{https://www.rit.edu/news/wayfair-gifts-850000-servers-rits-computer-science-house}{\$1.2 million+ server hardware donation} from Wayfair's decommissioned datacenter.\\ \smallskip
%•  Featured in a \href{https://cloud.google.com/blog/transform/wayfair-server-donation-mass-open-cloud-rit-student-innovation-johonnot}{Google Cloud article}.\\ \smallskip
%•  Currently maintaining the hardware and software for a student-run datacenter. Services include an OKD 4 Kubernetes cluster, Proxmox cluster, FreeIPA user management, Ceph distributed storage, multiple databases, mail server, MediaWiki instance, and various web services.}

%\cvmultiactivityra{Reporter Magazine \faCameraRetro}
%{Web Developer \& Sysadmin} {May 2021 - May 2023}
%{Responsible for maintaining the frontend and infrastructure for \href{https://reporter.rit.edu}{reporter.rit.edu}}.
